\section{Related Work}
\label{sec:related_work}

\paragraph{Knowledge Editing.}
ROME \citep{meng2022locating} performs rank-one updates to MLP weight matrices at a critical layer, treating factual knowledge as key-value associations in a linear associative memory.
MEMIT \citep{meng2022mass} extends this to multi-layer distributed editing.
More recent approaches include PMET \citep{li2024pmet} and constrained fine-tuning \citep{zhu2020modifying}.
Knowledge neurons \citep{dai2022knowledge} identify individual neurons associated with facts at a different granularity than our subspace-level analysis.
These methods implicitly assume that edited parameter-space directions correspond to knowledge storage locations---an assumption the localization-editing disconnect \citep{hase2023does} calls into question.

\paragraph{Training Data Attribution.}
Influence functions \citep{koh2017understanding} approximate leave-one-out effects but scale poorly and exhibit fragility on deep networks \citep{basu2021influence}.
TRAK \citep{park2023trak} projects gradients for tractability.
\citet{wang2024influence} document failure modes on LLMs.
MDA \citep{kwon2024mda} decomposes influence into subspace components, and RIF \citep{tang2025rif} shows accuracy depends critically on effective dimensionality.
Rather than improving attribution, we characterize the geometric properties of attribution gradients relative to an independent knowledge probe (editing).

\paragraph{Localization-Editing Disconnect.}
\citet{hase2023does} demonstrated that knowledge localization does not reliably predict editing success.
We address a related but distinct question: Hase et al.\ study whether localization predicts editing success (behavioral), while we study whether editing and attribution directions share geometric structure (geometric).
Both findings point to different knowledge operations accessing different parameter-space structures.

\paragraph{Parameter-Space Geometry.}
Loss landscape analysis \citep{li2018visualizing}, mode connectivity \citep{draxler2018essentially,frankle2020linear}, probing \citep{hewitt2019structural}, and embedding geometry \citep{ethayarajh2019contextual} have yielded insights about neural network parameter spaces.
However, the geometry of directions associated with specific knowledge operations has not been studied.

\paragraph{Unified Knowledge Perspectives.}
Recent surveys \citep{zhang2025unified} unify editing and attribution methodologically but not geometrically.
MAGIC \citep{zhao2025magic} shows attribution quality varies with retrieval methods, motivating our attribution quality analysis.
None examines whether parameter-space directions from different knowledge operations are geometrically commensurable.
